Figures

### 2020-05-05 PPP/Figures.Rmd
figures udpate

```{r}
library(tidyverse); options(tibble.width = Inf)
library(magrittr)
library("greta")
```

@@

```{r}

@@

>>>>

```{r}
library(tidyverse); options(tibble.width = Inf)
library(magrittr)

@@

```{r}
library("greta")

@@

```{r}
set.seed(1)
n <- 1000
df <- tibble(x = rnorm(n), y = rnorm(n, sd = 3)) 
big_n <- 100000
full_df <- tibble(x = rnorm(big_n), y = rnorm(big_n, sd = 3))

full_df %>% 
  ggplot() + 
  stat_density_2d(aes(x, y, fill = ..level..), geom = "polygon", alpha = 0.5) + 
  # geom_point(aes(x_data, y_data)) + 
  scale_fill_distiller(palette=1, direction=1) + 
  theme(
    legend.position = 'none',
    axis.title = element_blank(),
    axis.text = element_blank()
  )

<!-- ```{r} -->
<!-- full_df_with_data <- full_df %>%  -->
<!--   mutate(x_data = rep(df$x[1], 100000)) %>%  -->
<!--   mutate(y_data = rep(df$y[1], 100000))  -->

<!-- full_df_with_data %>%  -->
<!--   ggplot() +  -->
<!--   stat_density_2d(aes(x, y, fill = ..level..), geom = "polygon", alpha = 0.5) +  -->
<!--   geom_point(aes(x_data, y_data)) + -->
<!--   scale_fill_distiller(palette=1, direction=1) +  -->
<!--   theme( -->
<!--     legend.position = 'none', -->
<!--     axis.title = element_blank(), -->
<!--     axis.text = element_blank() -->
<!--   ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- full_df_with_data <- full_df %>%  -->
<!--   mutate(x_data = c(df$x[3], rep(df$x[1], 100000 - 1))) %>%  -->
<!--   mutate(y_data = c(df$y[3], rep(df$y[1], 100000 - 1))) -->

<!-- full_df_with_data %>%  -->
<!--   ggplot() +  -->
<!--   stat_density_2d(aes(x, y, fill = ..level..), geom = "polygon", alpha = 0.5) +  -->
<!--   geom_point(aes(x_data, y_data)) + -->
<!--   scale_fill_distiller(palette=1, direction=1) +  -->
<!--   theme( -->
<!--     legend.position = 'none', -->
<!--     axis.title = element_blank(), -->
<!--     axis.text = element_blank() -->
<!--   ) -->

<!-- ``` -->

```{r}
full_df_with_data <- full_df %>% 
  mutate(x_data = c((df$x / 1.7), rep(0, (100000 - 1000)))) %>% 
  mutate(y_data = c((df$y / 1.7), rep(0, (100000 - 1000))))

full_df_with_data %>% 
  ggplot() + 
  stat_density_2d(aes(x, y, fill = ..level..), geom = "polygon", alpha = 0.5) + 
  geom_point(aes(x_data, y_data)) +
  scale_fill_distiller(palette=1, direction=1) + 
  theme(
    legend.position = 'none',
    axis.title = element_blank(),
    axis.text = element_blank()
  )

```{r}
full_df_with_data <- full_df %>% 
  mutate(x_data = c((df$x / 1.7), rep(0, (100000 - 1000)))) %>% 
  mutate(y_data = c((df$y / 1.7), rep(0, (100000 - 1000))))

full_df_with_data %>% 
  ggplot() + 
  geom_point(aes(x_data, y_data)) +
  theme(
    legend.position = 'none',
    axis.title = element_blank(),
    axis.text = element_blank()
  ) + 
  theme_void()
